---
title: "Financial Statements and Ratios Assignments"
date: 
output:
  rmdformats::html_clean:
    highlight: kate
---

```{r knitr_init, echo=FALSE, cache=FALSE}
library(knitr)
library(rmdformats)

## Global options
options(max.print="75")
opts_chunk$set(echo=FALSE,
	             cache=TRUE,
               prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
opts_knit$set(width=75)
```

<!---
```{r}
source("https://raw.githubusercontent.com/Matt-Brigida/IEX_API_R_Wrapper/master/iex_api.R")
```
-->

# Financial Statement Assignment

Use [the app here](https://www.5minutefinance.org/concepts/an-introduction-to-financial-statements) to find a company with negative net income and a positive cash flow.

-  Upload a file with the company's name (ticker) and quarter in which this occurred. 
-  Can you explain what caused this in the particular case you found (or at least why this might occur in general)?

# Financial Ratios Assignment

Choose two companies, and use [the app here](https://www.5minutefinance.org/concepts/financial-ratios) to compare them using financial ratios.

- Choose your own companies.  Do not use the same two companies as anyone else in the class.
- Download images of the ratios (click the three bars in the uppr right of the app) and upload them to the assignment folder in Dropbox.
- Write any conclusions you can draw from your comparison.
